The Success of College Basketball Teams can be predicted using several advanced team statistics

### 2022-04-21 Paper-On-NCAAB-Stats/outputs/paper/Paper-On-NCAAB-Stats.Rmd
test

---
title: "The Success of College Basketball Teams can be predicted using several advanced team statistics"
subtitle: "A Linear Model Approach"
author: 
  - Thomas D'Onofrio
thanks: "Code and data are available at: https://github.com/TDonofrio62/Paper-On-NCAAB-Stats."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

@@

Unfortunately, there are some implications with these findings.

>>>>

---
title: "The Success of College Basketball Teams can be predicted using several advanced team statistics"
subtitle: "A Linear Model Approach"
author: 
  - Thomas D'Onofrio
thanks: "Code and data are available at: https://github.com/TDonofrio62/Paper-On-NCAAB-Stats."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The March Madness college basketball tournament is one of the most exciting sports events in the world due to the intense games, unpredictable results, and the creation of brackets by millions. In this paper, data displaying each college basketball schools’ advanced team statistics was used to create a linear model with team winning percentage as the response variable, where the explanatory variables are the team statistics that play the largest factor in leading to team success. It was found that [insert statistics here once model has been created] are the most important team statistics that affect the amount of wins a team gets the most, meaning fans can use these statistics to fill out their brackets more successfully. Unfortunately, the data is slightly biased due to inconsistent scorekeeping across teams and arenas, and the racial biases of referees when calling fouls, causing some implications to the findings."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
library(dplyr)
library(knitr)
```

@@

Unfortunately, there are some implications with these findings. There appears to be several aspects of bias in the datasets being used. For one, there is a lot of human error in the tracking of statistics by scorekeepers, causing certain ambiguously defined statistics in the data to be incorrectly tracked and thus skewed [@citeWilliams]. This means that data is tracked differently for each team in the league in their respective arenas, made evident by Madison Square Garden’s scorekeepers overstating the quality of shots in the NHL [@citeMcCurdy]. Thus, the data for some teams may be biased, making them look either better or worse relative to the other teams in the league. There is also unfortunate racial biases in basketball, as referees tend to show racism by calling more fouls on players with different races than them, leading to these teams scoring less points in games where this racial injustice occurs [@citeWolfers]. With more white referees in the league, teams with more white players may have team statistics skewed to make them seem better than they truly are, where teams with more players of colour will look worse because of the bias. We must be aware that our findings have been affected by these biases and as a result may not be perfectly correct. Nevertheless, a lot can be learned from the datasets which are still quite informative.
